---
title: "Binomial Package Vignette"
author: "Tyler Choe"
date: "2019-5-2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
library(ggplot2)
```

## Binomial Distribution
This R package '"binomial"' is an implementation for several functions for calculating prabilites of a Binomial random variable, and several calculations.

## Initialization of Data

A binomial distribution object is first created through a '"bindis"' object with the function 'bin_distribution(trials, prob)':

```{r}
bin1 <- bin_distribution(5, .5)
bin1
```

'bin_distribution' creates a data frame based on the input parameters with a success column from 0 to the number of trials inputted along with a column for the probability for each amount of successes based on the binomial formula.

You may obtain a dataframe with an additional cumulative column which aggregates the probabilities in order by calling the function 'bin_cumulative':

```{r}
bin2 <- bin_cumulative(5, .5)
bin2
```

## Summary Statistics for variable


Using the functions 'bin_mean()', 'bin_variance()', 'bin_mode()', 'bin_skewness()', 'bin_kurtosis()', you can obtain several summary measures about a binomial variable by passing in the number of trials and probability.

You are also able to see all of the measures in a condensed form by first creating a 'binvar' object by calling bin_variable(trials, prob).

```{r}
bin3 <- bin_variable(5, .5)
bin3
```

By calling summary on the binvar object, the function returns a named list-like summary.binvar object which includes all of the previously mentioned measures.

```{r}
binsum1 <- summary(bin3)
binsum1
```

## Visualizaion of binomial distributions

You may call plot() on the 'bindis' and 'bincum' objects to obtain visualizations for these two binomial implementations to have a better understanding of these distributions.

```{r}
plot(bin1)
plot(bin2)
```
